---
title: Dashboards in RStudio
author: Jorge Fitzmaurice Torres
date: '2017-09-29'
slug: dashboards-in-rstudio
categories:
  - Lahman
  - RStudio
  - dashboards
tags:
  - filter
  - ggplot2
  - select
  - str
  - graphics
  - dplyr
  - flexdashboard
---

This post will be about how to create a dashboard of visualizations in RStudio using dplyr, the Lahman database, ggplot2 for the visualizations, and flexdashboard for creating the dasboard.

First let's load some packages:

```{r message=FALSE,warning=FALSE}
library(Lahman)
library(dplyr)
library(ggplot2)
library(flexdashboard)
```

The visualizations we want to put on a dashboard usually has to have something in common, and this is why we chose Babe Ruth to create this dashboard.

First we need to extract the data I want for this visualization:

```{r}
result<-Batting%>%
        filter(playerID=='ruthba01')%>%
        select(SO,HR,yearID)

result
```

Then we need to create the visualization.

The first visualization will be a scatterplot:

```{r}
ggplot()+
  geom_point(data=result, aes(x=SO,y=HR))+
  xlab("Strikeouts")+
  ylab("Homeruns")
```

The second visualization will be a histogram:

```{r}
ggplot()+
  geom_histogram(data=result,aes(x=HR),bins=5, color="blue",fill="white" )+
  xlab("Homeruns")+
  ylab("Count")
```

The third visualization will be a time series:

```{r}
ggplot()+
  geom_point(data=result,aes(x=yearID,y=HR))+
  geom_line(data=result,aes(x=yearID,y=HR))+
  xlab("Year")+
  ylab("Homeruns")
```

Now we procede to creating the dashboard as an Rmd file with all the visualizations in it. You can see the post to the following link:

https://jfitzm43.github.io/dashboard/
