---
title: Bar Plots in RStudio
author: Jorge Fitzmaurice Torres
date: '2017-09-25'
slug: bar-plots-in-rstudio
categories:
  - ggiraph
  - Lahman
  - ggplot2
  - RStudio
tags:
  - filter
  - ggplot2
  - select
  - bar
  - str
  - factor
---

In this plot we will create an interactive bar plot with the Lahman database, dplyr, ggiraph, and ggplot2:
  

First let's load some packages:

```{r warning=FALSE, message=FALSE}
library(Lahman)
library(dplyr)
library(ggplot2)
library(ggiraph)
```

Now let's create a data frame to be able to work with ggplot, and ggiraph later.

```{r}
df<-Teams%>%
  filter(yearID==1980)%>%
  select(name,HR)%>%
  arrange(HR)

head(df)
```

The column name is a character, and we need to make it a factor (category) in order to be able to put the bar plot in order:

```{r}
class(df$name)

df$name<-factor(df$name, levels=df$name)

class(df$name)
```

This is to check that the names are in the order we want it to be:

```{r}
levels(df$name)
```

Now we create the interactive bar plot with the following code:

```{r}
g<-ggplot()+
  geom_bar_interactive(data=df, aes(x=name,y=HR, tooltip=HR,data_id=name),stat="identity", color="blue", fill="white")+
  coord_flip()+
  ggtitle("1980 Team Homeruns")+
  ylab("Homeruns")+
  xlab("Team")

ggiraph(code=print(g),hover_css = "fill:red; stroke:red")
```