---
title: Scatter Plot in Rstudio
author: Jorge Fitzmaurice Torres
date: '2017-09-22'
slug: scatter-plot-in-rstudio
categories:
  - dplyr
  - Lahman
  - RStudio
  - ggplot2
  - ggiraph
tags:
  - filter
  - select
  - ggplot2
  - summarize
  - ggiraph
---

In this class we will learn how to create a scatter plot with the Lahman database, 
using dplyr, and using ggplot2, with ggiraph to make it interactive.

First let's load some packages:

```{r warning=FALSE, message=FALSE}
library(Lahman)
library(dplyr)
library(ggplot2)
library(ggiraph)
```

Using dplyr, we want to get all the players with 400 or more HR in their careers, and the 
total amount of SO in their careers.

```{r}
df<-Batting%>%
  group_by(playerID)%>%
  summarize(career_HR=sum(HR), career_SO=sum(SO))%>%
  filter(career_HR>=400 )

df
```

We need to use a join to get the names and last names of the players.

```{r}
HR_vs_SO<-inner_join(df,Master,by=c('playerID'))%>%
  select(nameFirst,nameLast,career_HR,career_SO)

HR_vs_SO$name<-paste(HR_vs_SO$nameFirst, HR_vs_SO$nameLast)

HR_vs_SO
```

If we want to plot the data in ggplot2 to get an interactive scatter plot we use the following code:

```{r}
g<-ggplot()+
  geom_point_interactive(data=HR_vs_SO,aes(x=career_SO,y=career_HR,tooltip=name, data_id=nameLast))+
  ggtitle("Career Homeruns vs. Strikeouts for Great Hitters")+
  xlab("Career Strikeouts")+
  ylab("Career Homeruns")

ggiraph(code=print(g),hover_css = "fill:white;stroke:black")
```

